A Motion Blur Resilient Fiducial For Quadcopter Imaging

### 2014-11-10 WACV/paper.tex
WACV Final Copy
Added links to project web page and You Tube video.

%\wacvfinalcopy % *** Uncomment this line for the final submission

@@

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifwacvfinal\pagestyle{empty}\fi
\begin{document}
\title{A Motion Blur Resilient Fiducial For Quadcopter Imaging}
\maketitle

@@

We have implemented our algorithm in C++ using the OpenCV library.
Experiments were performed on a laptop with Intel Core i7
processor(@3.4GHz) and 4GB RAM.  Source code to generate and recognize
the code, as well as the data sets used in this paper will be made
publicly available.
%Video clips of collected data are provided in the supplementary
%material.
% Meghshyam: Is it a desktop PC or a laptop?

@@

  \includegraphics[width=0.4\linewidth]{images/output_10.jpg}
  \includegraphics[width=0.4\linewidth]{images/output_11.jpg}
  \caption{Sample outputs. The class label shown is the decimal equivalent
  of the binary coded fiducial.}
  \label{fig:out_outputs}
\end{figure}

@@

In another setup we arranged our fiducials on four sides of a box and
revolved the quadcopter around the box (see the supplementary video). Later, we
repeated the process by replacing our fiducial by ARTags. Figure~\ref{fig:setup} shows some
frames from this sequence as well as the performance of both
fiducials. The overall detection rate of our tags is 90\% while that
of ARTags is only around 60\%.

>>>>

\wacvfinalcopy % *** Uncomment this line for the final submission

@@

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifwacvfinal\pagestyle{empty}\fi
\begin{document}
\title{A Motion Blur Resilient Fiducial For Quadcopter Imaging}

\author{Meghshyam G. Prasad\\
Dept. of Computer Science, IIT Bombay\\
{\tt\small meghshyam@cse.iitb.ac.in}
\and
Sharat Chandran\\
Dept. of Computer Science, IIT Bombay\\
{\tt\small sharat@cse.iitb.ac.in}
\and
Michael S. Brown\\
School of Computing, NUS\\
{\tt\small brown@comp.nus.edu.sg}
}
\maketitle

@@

We have implemented our algorithm in C++ using the OpenCV library.
Experiments were performed on a laptop with Intel Core i7
processor(@3.4GHz) and 4GB RAM. (Please check author's webpage
\url{http://www.comp.nus.edu.sg/~mgprasad/fiducial/} for details of source code
and all datasets)
%Video clips of collected data are provided in the supplementary
%material.
% Meghshyam: Is it a desktop PC or a laptop?

@@

  \includegraphics[width=0.4\linewidth]{images/output_10.jpg}
  \includegraphics[width=0.4\linewidth]{images/output_11.jpg}
  \caption{Output of our fiducial detection algorithm on sample images. The
  class label shown is the decimal equivalent of the binary coded fiducial.}
  \label{fig:out_outputs}
\end{figure}

@@

In another setup we arranged our fiducials on four sides of a box and
revolved the quadcopter around the box (See video uploaded at \cite{video}).
Later, we repeated the process by replacing our fiducial by ARTags. Figure~\ref{fig:setup} shows some
frames from this sequence as well as the performance of both
fiducials. The overall detection rate of our tags is 90\% while that
of ARTags is only around 60\%.
